Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-09 Paper/paper.tex
Fixing a setnence that is broken

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environmenta local health board could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

>>>>

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.
Further work could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.
